\chosentitle

### 2024-10-08 paper/main.tex
update basis vectors plot

% Other possible titles
%\newcommand{\chosentitle}{Constrained linear models for stellar spectroscopy}
%\newcommand{\chosentitle}{Constrained linear absorption models for stellar spectroscopy}
%\newcommand{\chosentitle}{The Unreasonable Effectiveness of Linear Models in Stellar Spectroscopy}
%\newcommand{\chosentitle}{Stellar continuum modelling}
\newcommand{\chosentitle}{Constrained linear models for stellar spectroscopy}

@@

\section*{}\noindent\todo{
Known issues to resolve before submission:\\
- Show basis vectors from HARPS instead of APOGEE\\
- Update HARPS fits to use blaze-corrected flux (only AB-type stars use it now)\\
- In the "alpha Cen A" sample, sometimes they accidentally observed alpha Cen B and didn't realise! Maybe better to use a different star?\\
- Add citations\\
- Update red text.
}

@@

\begin{figure*}
    \includegraphics*[width=\textwidth]{nmf_plot.pdf}
    \caption{A schematic showing some basis vectors computed by non-negative matrix factorization from a grid of theoretical stellar spectra. \todo{Update this for BOSZ spectra, not APOGEE.}\label{fig:schematic}}
\end{figure*}

>>>>

% Other possible titles
%\newcommand{\chosentitle}{Constrained linear models for stellar spectroscopy}
%\newcommand{\chosentitle}{Constrained linear absorption models for stellar spectroscopy}
%\newcommand{\chosentitle}{The Unreasonable Effectiveness of Linear Models in Stellar Spectroscopy}
%\newcommand{\chosentitle}{Stellar continuum modelling}
\newcommand{\chosentitle}{Constrained linear absorption models for stellar spectroscopy}

@@

\section*{}\noindent\todo{
Known issues to resolve before submission:\\
- Update HARPS fits to use blaze-corrected flux (only AB-type stars use it now)\\
- In the "alpha Cen A" sample, sometimes they accidentally observed alpha Cen B and didn't realise! Maybe better to use a different star?\\
- Add citations\\
- Update red text.
}

@@

\begin{figure*}
    \includegraphics*[width=\textwidth]{harps-basis-vectors.pdf}
    \caption{A schematic showing a small wavelength range of the basis vectors computed by non-negative matrix factorization from a grid of theoretical stellar spectra.\label{fig:schematic}}
\end{figure*}
